---
title: "GitGV"
output: html_document
---
```{r}
install.packages("dpylr")
install.packages("shinydashboard")
library(shinydashboard)
library(ggplot2)
library(dplyr)
library(readr)
```

```{r}

```

```{r}
library(janitor)

dig <- read.csv("DIG.csv") %>%
  janitor::clean_names()
dig
```

Age vs Sex comparsion:

```{r}
#Age vs sex Comparision

library(shiny)
library(shinydashboard)
library(ggplot2)
library(readr)
library(dplyr)
library(janitor)

dig <- read_csv("DIG.csv") %>%
  janitor::clean_names()

ui <- dashboardPage(
  dashboardHeader(title = "DIG COMPARISON"),
  
  dashboardSidebar(
    sidebarMenu(
      menuItem("Age and Sex comparison", tabName = "comparison", icon = icon("users"))
    )
  ),
  
  dashboardBody(
    tabItems(
      tabItem(
        tabName = "comparison",
        fluidRow(
          box(width = 6, title = "Age distribution by sex",status = "primary",
              plotOutput("age_sex_plot")),
          
          box(width = 6 , title = "Summary table", status = "info",
              tableOutput("sex_age_summary"))
        )
      )
    )
  ) 
)

# --server--

server <- function(input,output,session) {
  
  output$age_sex_plot <- renderPlot({
    ggplot(dig, aes(x=age, fill = as.factor(sex))) +
      geom_histogram(alpha = 0.6 , bins = 30 , position = "identity") +
      labs(
        x = "Age",
        y = "Count",
        fill = "Sex",
        title = "Distribution of Age by sex"
      ) +
      theme_minimal()
  })
  
  output$sex_age_summary <- renderTable({
    dig %>%
      group_by(sex) %>%
      summarise(
        count = n(),
        mean_age = round(mean(age, na.rm = TRUE), 1),
        median_age = median(age, na.rm = TRUE),
        min_age = min(age, na.rm = TRUE),
        max_age = max(age, na.rm = TRUE)
      )
  })
}



shinyApp(ui, server )

```

Interpretation:

 I loaded the  DIG.csv data and made all the columns as lowercase and I built a shiny dashboard ui to display the age vs sex comparison and the server generate the histogram of age and sex and i also added the summary  table for min,max,median,mean for age per sex.Finally this code runs an shinyapp() which will show the plots and table summary.
 
 
 
 

Next question:



AGE VS DIABETES:
```{r}

library(shiny)
library(shinydashboard)
library(ggplot2)
library(dplyr)
library(readr)
library(janitor)

dig <- read.csv("DIG.csv") %>%
  janitor::clean_names()


# --- mutating a another column for age categories(it will be better for pie chart)---

dig_mut1 <- dig %>%
  mutate(age_group =
           case_when(
             age < 50 ~ "Below 50"  ,
             age >= 50 & age < 70  ~ "50-69",
             age >= 70 ~ "70+" )
           )


ui <- dashboardPage(
  dashboardHeader(title = "AGE vs DIABETES - pie chart"),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Age  and diabetes", tabName = "age_diabetes" , icon = icon("pie-chart"))
    )
  ),
  
  dashboardBody(
    tabItems(
      tabItem(
        tabName = "age_diabetes" , 
        
        fluidRow(
          box(
            width = 6,  status = "primary", title = "Pie chart : Age Group vs Diabetes" ,
            plotOutput("age_diabetes_pie")
            
          ),
          
          box( 
            width = 6 , status = "info" , title = "Summary Table" , 
            tableOutput("age_diabetes_table")
          ),
          
        )
      )
    )
  )
  
)

server <- function(input , output , session) {
  
  output$age_diabetes_pie <- renderPlot({
    
    pie_data <- dig_mut1 %>%
      group_by(age_group , diabetes) %>%
      summarise(count = n()) %>%
      ungroup()
    
    
    ggplot(pie_data, aes(x = "", y = count, fill = interaction(age_group, diabetes))) +
      geom_col(width = 1)+
      coord_polar("y", start = 0)+
      labs(
        fill = "Age Group + Diabetes",
        title = "Age Group vs Diabetes (Pie Chart)"
      ) +
      theme_void()
  
  })
 
  
  output$age_diabetes_table <- renderTable({
    dig_mut1 %>%
      group_by(age_group, diabetes) %>%
      summarise(
        count = n(),
        mean_age = round(mean(age),1 )
      )
  })
  
   
 }

shinyApp(ui,server)



```
Interpretation:

 I mutated a data frame called "dig_mut1" for better visualization diabetes age in pie chart and and I built a shiny dashboard code to represent the age and diabetes of the patient  and I created a server page  consisting of pie-chart visualization of the data and I made summary table for better understanding of age groups,so This code will show the age vs diabetes pie-chart visualization and a summary table ..
 
 
 Next question:
 
 Age vs Hypertension:
 
```{r}
library(shiny)
library(shinydashboard)
library(ggplot2)
library(dplyr)
library(janitor)

dig_mut1

ui <- dashboardPage(
  dashboardHeader(title = "Hypertension vs Age - Pie Chart"),
  
  dashboardSidebar(
    sidebarMenu(
      menuItem("Age vs Hypertension(Pie Chart)", tabName = "hypertension_age", icon = icon("pie-chart"))
    )
  ),
  dashboardBody(
    tabItems(
      tabItem(
        tabName = "hypertension_age",
        
        fluidRow(
          box(width = 6 , title = "hypertension ditribution from Age Group",
              status = "primary", plotOutput("pie_chart")) , 
          
          box(width = 6 , title = "Summary table",
              status = "info", tableOutput("pie_summary"))
          
        )
      )
    )
  )
  
)


server <- function(input , output, session) {
  
  output$pie_chart <- renderPlot({
    
    pie_data <- dig_mut1 %>%
      group_by(age_group) %>%
      summarise(hypertension_count = sum (hyperten == 1, na.rm = TRUE))
    
    ggplot(pie_data, aes( x = "", y = hypertension_count, fill = age_group)) +
      geom_col(width = 1) +
      coord_polar(theta = "y") +
      labs(title = "Hypertension cases by Age Group", fill = "Age Group") +
      theme_void()
  })
  
  output$pie_summary <- renderTable({
    
    dig_mut1 %>%
      group_by(age_group) %>%
      summarise(
        total = n(),
        hypertension_cases = sum(hyperten == 1, na.rm = TRUE),
        hypertension_percent = round(hypertension_cases/ total *100,1)
      )
  }) 
  
}


shinyApp(ui, server)

```
 Interpretation:
 
  I took that mutated data frame ("dig_mut1") as my dataset because I added a column for better age visualization  and I built a code for Age vs Hypertension(history of hypertension) and code is similar to my last code (age vs diabetes) .In this code i added an extra column in summary table (percent of hypertension cases from the age groups), the code will show that pie chart of age vs hypertension and a summary table with data of the pie chart..
 
Age vs Race
```{r}
#Comparison of Age with Race
library(shiny)
library(shinydashboard)
library(ggplot2)
library(readr)
library(dplyr)
library(janitor)

#Gathering the data
dig <- read.csv("DIG.csv")%>%
  clean_names()

ui<- dashboardPage(
  dashboardHeader(title = "DIG: Age vs Race"),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Age vs Race", tabName ="Age_and_Race", icon= icon("users")))),
  dashboardBody(
    tabItems(
      tabItem(
        tabName= "Age_and_Race",
        fluidRow(
          box(
            width=6,
            title= "Age distribution by Race data",
            status= "primary",
          plotOutput("age_vs_race_plot")),
          box(
            width=6,
            title = "Summarising age by race data",
            status="info",
          tableOutput("summarising_age_vs_race")
          )
          )
        )
      )
    )
  )

server<- function(input, output, session) {
  
  #plotting a histogram to visualise the data
  output$age_vs_race_plot <- renderPlot({
    ggplot(dig, aes(x= age, fill = factor(race)))+
      geom_histogram(
        bins= 30,
        position = "identity",
        alpha= 0.8
      )+
      labs(
        x= "Age(years)",
        y= "Number of patients",
        fill= "Race",
        title = "Distribution of age by race")+
      theme_minimal()
  })
  
#summarising the age table by race
  output$summarising_age_vs_race <- renderTable({
    dig %>%
      group_by(race) %>%
      summarise(
        n = n(),
        mean_age = round(mean(age, na.rm = TRUE),1),
        median= median(age, na.rm = TRUE),
        min_age = min(age, na.rm = TRUE),
        max_age = max(age, na.rm = TRUE),
        .groups = "drop"
      )
  })
}

shinyApp(ui=ui,server = server)
```
Interpretation:
In this analysis, I used the DIG dataset where the age distributions are quite higher and similar to the race groups.
From both the race categories, the mean ages has been lying in the mid 60s with similar median and ranges, which is suggesting that all the patients from the different racial group enrolled in the study at a age that was comparable between each other.Although there are many patients in Race 1 than in Race group 2, the appearance of the histograms and the summary statistics had no major age imbalance between the races.

Comparing Weight and Blood group of the DIG dataset
```{r}
library(shiny)
library(shinydashboard)
library(ggplot2)
library(readr)
library(dplyr)
library(janitor)

#Cleaning the dataset 
dig<- read.csv("DIG.csv") %>%
  clean_names()

ui <- dashboardPage(
  dashboardHeader(title=" DIG:BMI and Race"),
  dashboardSidebar(
    sidebarMenu(
      menuItem("BMI vs Race",
               tabName = "bmi_race",
               icon= icon("user"))
    )
  ),
  dashboardBody(
    tabItems(
      tabItem(
        tabName = "bmi_race",
        fluidRow(
          box(
            width=6,
            status = "primary",
            title= "Summary of BMI by race",
            plotOutput("bmi_race_box")),
          box(width = 6, status="info", title = "Summary of BMI by race",
              tableOutput("bmi_race_summary")
          )
        )
      )
    )
  )
)

server <- function(input, output,session) {
  
  #plotting a boxplot to visualise the data for each race group
  output$bmi_race_box <-renderPlot({
    ggplot(dig,aes(x=factor(race),y= bmi,fill=factor(race)))+
      geom_boxplot(alpha=0.7, outlier.alpha = 0.6)+
      labs(
        x="Race",
        y="BMI",
        fill="Race",
        title = "Distribution of BMI by race"
      )+
      theme_minimal()
  })
  
  #summarising in a table
  output$bmi_race_summary <- renderTable ({
    dig %>%
      group_by(race) %>%
      summarise(
        n=n(),
        mean_bmi = round(mean(bmi, na.rm= TRUE),1),
        median= median(bmi,na.rm = TRUE),
        min_bmi= min(bmi, na.rm = TRUE),
        max_bmi= max(bmi, na.rm=TRUE),
        .groups= "drop"
      )
  })
}

shinyApp(ui=ui,server= server)
```
Interpretation:
With a similar code for the age vs race, I included a boxplot for the visualisation of bmi vs race. From the analysis done above, the BMI is very similar across both the racial groups of the trail, Both the groups have mean BMIs around 27 and almost similar medians, while the boxplot shows overlapping inter-quartile ranges and overall spread. Group 1 has many more patients than group 2 but their BMI distributions are shaped similar, with a same minimum and maximum values.Overall, there is no clear evidence of major difference in the BMI between the two racial categories in the dataset.

```{r}
names(dig)
```


Next Question:

ID vs NHOSP(number of hospitalisation):

```{r}

library(shiny)
library(shinydashboard)
library(ggplot2)
library(dplyr)
library(readr)
library(janitor)

dig

ui <- dashboardPage(
  dashboardHeader(title = "ID vs NHOSP"),
  
  dashboardSidebar(
    sidebarMenu(
      menuItem("ID and Hospitalisation", tabName = "id_hosp", icon = icon("hospital"))
    )
  ),
  
  dashboardBody(
    tabItems(
      tabItem(
        tabName = "id_hosp",
        
        fluidRow(
          box(
            width = 6, status = "primary", solidHeader = TRUE,
            title = "Histogram : Number of Hospitalisations",
            plotOutput("hosp_hist")
          ),
          
          box(
            width = 6 , status = "info", solidHeader = TRUE,
            title = "Summary of NHOSP",
            tableOutput("hosp_summary")
          )
        )
      )
    )
  )
  
 )




server <- function (input, output, session) {
  
  output$hosp_hist <- renderPlot({
    ggplot(dig, aes(x= nhosp)) +
      geom_histogram(fill = "red", color = "grey",bins = 20, alpha = 0.7)+
      labs(
        title = "Distribution of Number of hospitalisations",
        x = "NSHOP(Number of Hospitalisations)",
        y = "count of patients"
      ) +
      theme_minimal()
    
  })
  
  output$hosp_summary <- renderTable({
    dig %>%
      summarise(
        total_patients = n(),
        mean_hosp = round(mean(nhosp, na.rm = TRUE),1 ),
        median_hosp = median(nhosp, na.rm = TRUE),
        min_hosp = min(nhosp, na.rm = TRUE),
        max_hosp = max(nhosp,na.rm = TRUE)
      )
  })
  
  
}

shinyApp(ui,server)

```

